Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-26 paper-v1.tex
integrated corrections by @biancasama

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a decentralized content-addressable, peer-to-peer protocol which guarantees data immutability and unique file identification.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system still engages into maintaining the privacy of both authors and reviewers in a double-blind approach.

@@

\subsubsection{AntsReview}
AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}. It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet, and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
  \item to specify the amount of Ether for the reward that will be transferred from Alice to the contract.
\end{itemize}

@@

\subsubsection{Tokenomics}
AntsReview integrates a few ERC20 tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS, is the primary protocol ERC20 token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS, is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
\newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[9]{\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.

@@

EOA in Ethereum are controlled by private key. An user can send messages from an externally owned account by creating and signing a transaction. The limitation of this type of solution concerning the protocol's privacy is due to the fact that blockchain and transactions are public, therefore the details of transactions are visible to anyone by browsing a block explorer (like Etherscan), and are subjected to data mining that could extract value and identify users in the blockchain.
\newline To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol. In the future zkANTS could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.

>>>>

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system still engages into maintaining the privacy of both authors and reviewers in a double-blind approach.

@@

\subsubsection{AntsReview}
AntsReview (See Figure \ref{fig:contracts}\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}. It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS} and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
  \item to specify the amount of Ether for the reward that will be transferred from Alice to the contract.
\end{itemize}

@@

\subsubsection{Tokenomics}
AntsReview integrates a few \emph{ERC20}\footnote[8]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS, is the primary protocol ERC20 token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS, is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
\newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[9]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.

@@

EOA in Ethereum are controlled by private key. An user can send messages from an externally owned account by creating and signing a transaction. The limitation of this type of solution concerning the protocol's privacy is due to the fact that blockchain and transactions are public, therefore the details of transactions are visible to anyone by browsing a block explorer (like Etherscan), and are subjected to data mining that could extract value and identify users in the blockchain.
\newline To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol. In the future zkANTS could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Future developments will investigate viable solutions, for scaling the system, like \emph{ZK$^2$-Rollups}\footnote[10]{\emph{ZK-Rollups}.\textsc{URL:}\url{https://medium.com/aztec-protocol/aztec-fast-privacy-with-zk%C2%B2-rollup-7c742f45457}.} by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.
